---
title: "Report"
author: "Longhao Chen, Xiaolu Zhai,Yudi Mao, Tianying Xu"
date: "2018.10.18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

I. Data
For baseball attendance data, we download it from http://www.espn.com/mlb/team/schedule/_/name/bos.
For weather data, we download it from NOAA website, the url is https://www.ncdc.noaa.gov/cdo-web/datasets. The data includes a lot of index like temperature, windspeed,snowfall, and it starts at 2012 and ends at 2018.  
For basketball attendance data, we get the data from ESPN website using web crawler, with the url http://www.espn.com/nba/team/schedule/_/name/bos/season/2018. We use rvest package to craw the attendance data through 2012-2013 season to 2017-2018 season. 
```{r cars}
# web crawler of basketball attendance data
library(xml2)
library(rvest)
library(stringr)

# create null vector to record the data
Date_all <- c()
ATTD <- c()
CAP <- c()
Pr <- c()

# get urls
n1 <- 2013:2018
sites1 <- paste0("http://www.espn.com/nba/team/schedule/_/name/bos/season/", n1, "/seasontype/2")

for (i in 1:length(sites1)) {
  web <- read_html(sites1[i])

  Dates <- web %>%
    html_nodes('td[class=\"Table2__td\"] span') %>%
    html_text()

  # get Date
  for (m in 1:length(Dates)) {
    if (grepl(",", Dates[m]) == TRUE) {
      MD <- str_split(str_split(Dates[m], ",")[[1]][2], " ")
      if (MD[[1]][2] == "Oct" | MD[[1]][2] == "Nov" | MD[[1]][2] == "Dec") {
        Date_all <- c(Date_all, paste0(n1[i] - 1, ",", MD[[1]][2], ",", MD[[1]][3]))
      } else {
        Date_all <- c(Date_all, paste0(n1[i], ",", MD[[1]][2], ",", MD[[1]][3]))
      }
    }
  }

  # get url for attendance of each game
  hrefs <- web %>%
    html_nodes('div span[class=\"ml4\"] a') %>%
    html_attr("href")

  # get attendance data
  for (j in 1:length(hrefs)) {
    web1 <- read_html(hrefs[j])

    Ns <- web1 %>%
      html_nodes('div[class=\"game-info-note capacity\"]') %>%
      html_text()

    Attd <- str_split(Ns[1], ":")
    Attd_n <- as.numeric(str_c(str_split(Attd[[1]][2], ",")[[1]][1], str_split(Attd[[1]][2], ",")[[1]][2]))
    ATTD <- c(ATTD, Attd_n)

    Cap <- str_split(Ns[2], ":")
    Cap_n <- as.numeric(str_c(str_split(Cap[[1]][2], ",")[[1]][1], str_split(Cap[[1]][2], ",")[[1]][2]))
    CAP <- c(CAP, Cap_n)

    p <- min(Attd_n / Cap_n, 1)
    Pr <- c(Pr, paste0(round(p * 100, 3), "%"))
    print(paste0(n1[i], "-", j))
  }
}

Date1 <- Date_all[-which(Date_all == "2013,Apr,16")]
Date2 <- Date1[-which(Date1 == "2016,Jan,23")]
BD <- as.data.frame(t(rbind(Date2, ATTD, CAP, Pr)))

library(dplyr)
BD_F <- BD %>%
  filter(CAP == 18624)
write.csv(BD_F, "Celtics/Celtics.csv")
```

b. baseball

```{r}
library(readxl)
library(tidyverse)

# inport RedSox data
coltype <- c("numeric", "text", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "text", "numeric", "text", "text", "text", "text", "text", "text", "numeric", "text", "text")
RedSox_2012 <- read_excel("RedSox/RedSox_2012.xlsx", col_types = coltype)
RedSox_2012$year <- "2012"
RedSox_2013 <- read_excel("RedSox/RedSox_2013.xlsx", col_types = coltype)
RedSox_2013$year <- "2013"
RedSox_2014 <- read_excel("RedSox/RedSox_2014.xlsx", col_types = coltype)
RedSox_2014$year <- "2014"
RedSox_2015 <- read_excel("RedSox/RedSox_2015.xlsx", col_types = coltype)
RedSox_2015$year <- "2015"
RedSox_2016 <- read_excel("RedSox/RedSox_2016.xlsx", col_types = coltype)
RedSox_2016$year <- "2016"
RedSox_2017 <- read_excel("RedSox/RedSox_2017.xlsx", col_types = coltype)
RedSox_2017$year <- "2017"

# tidy RedSox date and attendance
RedSox <- rbind(RedSox_2012, RedSox_2013, RedSox_2014, RedSox_2015, RedSox_2016, RedSox_2017)
TidyDate <- RedSox$Date %>%
  str_remove("Monday ") %>%
  str_remove("Tuesday ") %>%
  str_remove("Wednesday ") %>%
  str_remove("Thursday ") %>%
  str_remove("Friday ") %>%
  str_remove("Saturday ") %>%
  str_remove("Sunday ") %>%
  str_remove(" \\(1\\)") %>%
  str_remove(" \\(2\\)") %>%
  paste(RedSox$year)
RedSox$DATE <- as.Date(TidyDate, format = "%b %d %Y")

RedSox_Tidy <- filter(RedSox, is.na(X__2)) %>%
  select(DATE, Attendance)

# get canceled games
RedSoxcg <- RedSox %>%
  filter(!is.na(`Orig. Scheduled`) & is.na(X__2)) %>%
  select(`Orig. Scheduled`) %>%
  mutate(DATE = as.Date(substr(`Orig. Scheduled`, 1, 10)), Attendance = 0)

RedSox_Tidy2 <- bind_rows(RedSox, RedSoxcg) %>%
  filter(is.na(X__2)) %>%
  select(DATE, Attendance)

# import Weather data
Weather <- read.csv("Weather/Weather_Data.csv")
Weather$DATE <- Weather$DATE %>%
  str_remove(" 23:59") %>%
  as.Date("%Y/%m/%d")
Weather$DAILYPrecip_num <- as.numeric(Weather$DAILYPrecip)


# join
RedSox_Join <- RedSox_Tidy %>%
  left_join(Weather, by = "DATE")

RedSox_Join2 <- RedSox_Tidy2 %>%
  left_join(Weather, by = "DATE")
```


II. Analysis
1. Baseball
a. data
Wrangled in the I.DATA part.

b. EDA
```{r}
ggplot(data = RedSox_Join, mapping = aes(x = DAILYMinimumDryBulbTemp, y = Attendance / max(Attendance))) +
  geom_point() +
  geom_smooth(se = FALSE, linetype = "dashed", color = "red")

ggplot(data = RedSox_Join2, mapping = aes(x = DATE, y = Attendance, color = DAILYPrecip_num)) +
  geom_point()
```


2. Basketball
a. data
We need to join the weather and basketball data together by date so that we could do EDA. We first translate the date of basketball and weather to the same format and join them, then clean data. (There are "T" in the value of index that means the number is too small to measure, thus we translate these values to be 0.)
```{r}
library(stringr)
library(dplyr)
library(ggplot2)

# Change date format for basketball data
Bskt <- read.csv("Celtics/Celtics.csv", header = T)
Date <- str_split(string = Bskt$Date2, ",")
Y <- c()
M <- c()
D <- c()
for (i in 1:length(Date)) {
  Y <- c(Y, Date[[i]][1])
  m <- Date[[i]][2]
  if (m == "Jan") {
    mm <- 1
  } else if (m == "Feb") {
    mm <- 2
  } else if (m == "Mar") {
    mm <- 3
  } else if (m == "Apr") {
    mm <- 4
  } else if (m == "Oct") {
    mm <- 10
  } else if (m == "Nov") {
    mm <- 11
  } else if (m == "Dec") {
    mm <- 12
  }

  M <- c(M, mm)
  D <- c(D, Date[[i]][3])
}
Date <- str_c(Y, M, D, sep = "-")
Bskt_f <- Bskt[, -c(1, 2)]
Bskt_f$Date <- Date

# change date format for weather data
Wth <- read.csv("Weather/weather_Data.csv", header = T)
DD <- str_split(string = Wth$DATE, " ")
W_Dt <- c()
for (i in 1:length(DD)) {
  A <- str_split(DD[[i]][1], "/")
  d <- str_c(A[[1]][1], "-", A[[1]][2], "-", A[[1]][3])
  W_Dt <- c(W_Dt, d)
}
Wth$Date_f <- W_Dt

# Join two data set together and clean data
df <- left_join(Bskt_f, Wth, by = c("Date" = "Date_f"))
ddd <- as.Date(df$Date)
df$Date <- ddd
df$feel_like_temp <- df$DAILYDeptFromNormalAverageTemp * df$DAILYAverageDryBulbTemp
for (i in 1:dim(df)[1]) {
  if (is.na(df$DAILYSnowfall[i])) {

  } else if (df$DAILYSnowfall[i] == "T") {
    df$DAILYSnowfall[i] <- 0
  }
}
for (i in 1:dim(df)[1]) {
  if (is.na(df$DAILYPrecip[i])) {

  } else if (df$DAILYPrecip[i] == "T") {
    df$DAILYPrecip[i] <- 0
  }
}
df$P <- df$ATTD / df$CAP
```

b. EDA
For weather data, we choose daily average normal temperature, daily average wind speed, daily average snow fall.

First we plot average attendance through each season. 
```{r}
library(ggplot2)
library(dplyr)
# data
p <- c()
for (i in 2013:2018) {
  dfdf <- df %>% filter(Date > as.Date(paste0(i - 1, "-7-1")) & Date < as.Date(paste0(i, "-6-30")))
  pp <- round(mean(dfdf$P), 3)
  p <- c(p, pp)
}
y <- c()
for (i in 2012:2017) {
  y <- c(y, paste0(i, "-", i + 1))
}

numericp <- (c(1, 0.972, .945, .981, .996, 1))


ggplot(youknow, mapping = aes(y, numericp)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(x = "Season", y = "Attendance(%)", title = "Attendance versus Seasons") +
  geom_text(aes(label = numericp)) +
  theme(plot.title = element_text(hjust = 0.5))
```


Then we plot attendance versus every weather variable to see the association between attendance and weather.
```{r}
library(ggplot2)
ggplot(df, mapping = aes(DAILYAverageDryBulbTemp, P)) +
  geom_point(colour = "royalblue3", shape = 16)
ggplot(df, mapping = aes(DAILYAverageWindSpeed, P)) +
  geom_point(colour = "royalblue3", shape = 16)
ggplot(df, mapping = aes(DAILYSnowfall, P)) +
  geom_point(colour = "royalblue3", shape = 16)
```

From the plots above, we could see that whatever the weather situation is, the attendance could still be high or low, there seems no correlation between weather situation and basketball attendance.

Finally we try to plot attendance versus two variables to see if there is interaction effects.
```{r}
library(ggplot2)
ggplot(df, mapping = aes(x = DAILYAverageDryBulbTemp, y = P, colour = DAILYAverageWindSpeed)) +
  geom_point(shape = 16) + ylab("Attendence rate") + xlab("Daily Average Temperature")
ggplot(df, mapping = aes(x = DAILYSnowfall, y = P, colour = DAILYAverageWindSpeed)) +
  geom_point(shape = 16)+ylab("Attendence rate") + xlab("Daily Snow Fall")
ggplot(df, mapping = aes(x = DAILYAverageDryBulbTemp, y = P, colour = DAILYAverageWindSpeed, size = DAILYSnowfall)) + 
  geom_point(shape = 16)
```

These three plots do not show any pattern and association of weather situation and attendance. In the final plot, most points with bigger size and lighter color, which means the snow is heavy and the wind speed is fast, are still correspond to the 100% attendance, which is not make sense. Thus weather situation and attendance are not correlated.










